withmice

### 2024-03-05 withmice.Rmd
new attempt to do mice

---
title: "withmice"
output:
  pdf_document:
    toc: yes
    toc_depth: 2
    keep_tex: yes
  header-includes:
  - \usepackage{dcolumn}
  - \usepackage{array}
  - "\\usepackage{placeins}"
  keep_md: yes
---

```{r load packages, warning = FALSE, message = FALSE, echo=FALSE}
  knitr::opts_chunk$set(warning = FALSE, message = FALSE)

suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(tidyr))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(lavaan))
suppressPackageStartupMessages(library(tsibble))
suppressPackageStartupMessages(library(DT))
suppressPackageStartupMessages(library(knitr))
suppressPackageStartupMessages(library(psych)) 
suppressPackageStartupMessages(library(foreign))
suppressPackageStartupMessages(library(MASS))
suppressPackageStartupMessages(library(Hmisc))
suppressPackageStartupMessages(library(reshape2))
suppressPackageStartupMessages(library(mice))

```

```{r setup, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

moduletwo <- read_excel(here::here("thesis_surveydata/political_factors_complete.xlsx"))
module2 <- data.frame(moduletwo)
module2[module2 == "Rather not say/ Don't know"] <- "Rather not say/Don't know"

# loaded data set for module 2 eco -pol variables and removes the rows with question number and question text
```

```{r, eval =TRUE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
#This chunk contains the coding schemes of various scales used in survey one: eco-political factors, kahan scale and acceptance scale
codedmodule2 <- module2 %>%

#remove row 1
  filter(!row_number() %in% c(1,2)) %>%

# replace risky likert scale with numbers
  mutate_at(vars(starts_with("Risky")), funs(case_when(. =="Not at all risky" ~ 1, 
                                                       . =="Slightly risky" ~ 2, 
                                                       . =="Moderately risky" ~ 3, 
                                                       . =="Very risky" ~ 4, 
                                                       . =="Extremely risky" ~ 5))) %>%

# replace beneficial likert scale with numbers  
  mutate_at(vars(starts_with("Ben")), funs(case_when(. =="Not at all beneficial" ~ 1,
                                                     . =="Slightly beneficial" ~ 2,
                                                     . =="Moderately beneficial" ~ 3,
                                                     . =="Very beneficial" ~ 4,
                                                     . =="Extremely beneficial" ~ 5 ))) %>%

# replace nuclear acceptance likert scale with numbers
  mutate_at(vars(N_accept,N_reluctantlyaccept,N_reject), funs(case_when(. == "Strongly disagree" ~ 1, 
                                                                        . == "Somewhat disagree" ~ 2,
                                                                        . == "Neither agree nor disagree" ~3,
                                                                        . == "Somewhat agree" ~ 4,
                                                                        . == "Strongly agree" ~ 5))) %>%

# code likert scale for variables for Kahan scale into numbers
  mutate_at(vars(starts_with (c("K_S","K_E","DISPLACE", "POLLUTE", "HEALTH", "JOBS", "BEAUTY", "PRIDE", "NPRIDE","DEVNUCLEAR","DEVSOLAR", "DEVCOAL","PROSPER", "RELY"))), funs(case_when(. == "Strongly disagree" ~ 1, 
               . == "Somewhat disagree" ~ 2,
               . == "Neither agree nor disagree" ~3,
               . == "Somewhat agree" ~ 4,
               . == "Strongly agree" ~ 5))) %>%

# NO reverse coding for likert scale for variables for Kahan scale into numbers
  mutate_at(vars(starts_with (c("K_H","K_I"))), funs(case_when(. == "Strongly disagree" ~ 1, 
                                                               . == "Somewhat disagree" ~ 2,
                                                               . == "Neither agree nor disagree" ~3,
                                                               . == "Somewhat agree" ~ 4,
                                                               . == "Strongly agree" ~ 5))) %>%

# code eco-pol scale variables into numbers
mutate_at(vars(SYSTEMDEMO,SYSTEMRELIGION,SYSTEMTECHNO,SYSTEMTOTAL,WEALTHLIM,MECHANISATION,DECISIONDECEN,INDUSTRYSMALL,ECONOMYLOCAL,ENVOVERDEV,OWNERPUB, OWNERREG), funs(case_when(. == "Strongly disagree" ~ 1, 
                        . == "Somewhat disagree" ~ 2,
                        . == "Neither agree nor disagree" ~3,
                        . == "Somewhat agree" ~ 4,
                        . == "Strongly agree" ~ 5))) %>%

# NO reverse code eco-pol scale variables into numbers 
 mutate_at(vars(DECISIONCEN,INDUSTRYLARGE,ECONOMYGLOBAL,OWNERPVT,OWNERNOREG, DEVOVERENV), funs(case_when(. == "Strongly disagree" ~ 1, 
                                                                                                         . == "Somewhat disagree" ~ 2,
                                                                                                         . == "Neither agree nor disagree" ~3,
                                                                                                         . == "Somewhat agree" ~ 4,
                                                                                                         . == "Strongly agree" ~ 5))) %>%
  mutate_all(~ifelse(. == "Rather not say/ Don't know", "Rather not say/Don't know", .))%>%
  mutate_all(~ifelse(. == "West bengal", "West Bengal", .))%>%
  mutate_all(~ifelse(. == "WEST BENGAL", "West Bengal", .))%>%
  mutate_all(~ifelse(. == "Up", "Uttar Pradesh", .))%>%
  mutate_all(~ifelse(. == "Tamilnadu", "Tamil Nadu", .))%>%
  mutate_all(~ifelse(. == "UP", "Uttar Pradesh", .))

```

```{r, echo=FALSE}

module2mice <- codedmodule2 %>%
              dplyr::select(starts_with (c("Risky_Nuclear", "Risky_Solar", "Risky_Coal", "Ben_Nuclear", "Ben_Solar", "Ben_Coal","K_S","K_E","DISPLACE", "POLLUTE", "HEALTH", "JOBS", "BEAUTY", "PRIDE", "NPRIDE","DEVNUCLEAR", "DEVSOLAR", "DEVCOAL","PROSPER", "RELY","K_H","K_I", "WEALTHLIM", "MECHANISATION", "DECISIONDECEN", "INDUSTRYSMALL", "ECONOMYLOCAL", "ENVOVERDEV", "OWNERPUB","OWNERREG", "DECISIONCEN", "INDUSTRYLARGE", "ECONOMYGLOBAL", "OWNERPVT", "OWNERNOREG", "DEVOVERENV", "age", "urban_rural", "gender", "caste", "religion", "State"))) %>%
              dplyr::select(!religiontext)

module2mice2 <- module2mice %>%
  mutate(across(starts_with("Risky_"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("Ben_"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("K_S"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("K_E"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("DISPLACE"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("POLLUTE"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("HEALTH"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("JOBS"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("BEAUTY"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("PRIDE"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("NPRIDE"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("DEV"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("PROSPER"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("RELY"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("K_H"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("K_I"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("WEALTHLIM"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("MECHANISATION"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("DECISIONDECEN"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("INDUSTRYSMALL"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("ECONOMYLOCAL"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("ENVOVERDEV"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("OWNERPUB"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("OWNERREG"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("DECISIONCEN"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("INDUSTRYLARGE"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("ECONOMYGLOBAL"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("OWNERPVT"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("OWNERNOREG"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("DEVOVERENV"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("age"), ~factor(.x, ordered = TRUE)))%>%
  mutate(across(starts_with("urban_rural"), ~factor(.x, ordered = FALSE)))%>%
  mutate(across(starts_with("gender"), ~factor(.x, ordered = FALSE)))%>%
  mutate(across(starts_with("caste"), ~factor(.x, ordered = FALSE)))%>%
  mutate(across(starts_with("religion"), ~factor(.x, ordered = FALSE)))%>%
  mutate(across(starts_with("State"), ~factor(.x, ordered = FALSE)))

str(module2mice2)

```

```{r, echo=FALSE}

## checking levels for all the variables

# Loop through each column in the dataframe
for(col_name in names(module2mice2)) {
  # Check if the column is a factor
  if(is.factor(module2mice2[[col_name]])) {
    # Print the levels of the factor
    cat("Levels for", col_name, ":\n")
    print(levels(module2mice2[[col_name]]))
    cat("\n") # Just for better readability in the output
  }
}
```

```{r, echo=FALSE}

d.pattern(module2mice2)

```

>>>>

---
title: "withmice"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
